\input sys/inputs.tex

\begin{document}

\bigheading{Shades of the town}

% \info{task_name}{infile}{outfile}{points}{timelimit}{memlimit}
% leave this values, if you are not interested
\info{shades}{stdin}{stdout}{100}{1000 ms}{1 GB}

Long time ago in a galaxy far far away was a town.
Well, we suppose it was a town.
But it disappeared. And it left almost nothing.
Just a shade. Dark, cold shade.
Shade which doesn't move.
Shade of the destiny.
Shade \dots  OK, lets work.
We want to know the heights of the buildings in the town.
(To calculate the population.)
But the heights of the shade may be scaled.
Luckily, we know some architecture specifics of the culture
which ocupied this planet.

All the buildings in the town stand in a single line,
with uniform widths and spaces beetwen them.
The only thing which changes is the heights.
There are some height paterns which are frequently used.

Your task is to find every pattern occurence in the shade
and output the number of occurences,
so we can decide whether paterns can help us.


\heading{Task}

The shade is a positive integer sequence of scaled heights.
The patern is an a positive integer sequence of heights.
We say that pattern occurs in the shade,
if there is an subsequence of shade, which can be scaled,
to be the same as the pattern.
Find out the number of the occurences
of the all patterns in the shade.
(One pattern can occur multiple times)


\heading{Input}

On the first line of input is a single integer $n$
-- the number of paterns.

Each of next $n$ lines describes one pattern.
It starts with an integer $l_i$ -- the patern lenght.
Then $l_i$ space separated positive integers follows.

The last line describes the shade.
It starts with an integer $m$ -- the shade lenght.
Then $m$ space separated positive integers follows.

\bigskip

It holds:\\
$1 \leq m \leq 3\cdot10^5$\\
$1 \leq l_i$\\
$\sum^{n}_{i=1} l_i \leq m$\\
All the sequence numbers are at most $10000$.

\smallskip

In the $40\%$ of testcases also holds $m \leq 1000$.

\heading{Output}

Output a line with single integer
-- the number of occurences of the patterns in the shade.

\heading{Samples}


\sampleIN
4
1 47
2 21 42
2 34 17
3 1 2 1
7 3 6 3 6 12 6 3
\sampleOUT
15
\sampleCOMMENT
The first patterns can be scaled to
each height and so occurs 7 times.
The second and the third patterns occurs each one 3 times.
The fourth pattern occurs 2 times.
\sampleEND


\end{document}