\input sys/inputs.tex

\begin{document}

\bigheading{Cutting of a birthday cake}

% \info{task_name}{infile}{outfile}{points}{timelimit}{memlimit}
% leave this values, if you are not interested
\info{cutting}{text files}{text files}{100}{-}{-}

Mimino is celebrating his birthday! Although an incredible programmer, he is only $N$ years old. His grandma cooked a huge chockolate cake for his birthday party and she placed $N$ candles on the top of it. Mimino and his friends are all getting really hungry, therefore he wants to cut the cake using as least straight cuts as possible. There can't be more than one candle on any slice. Being a perfectionalist, he has decided to write a program to minimize the number of cuts.

\heading{Task}

Having a plane and some points in it, give a set of lines that separate the plane into subplanes so that each subplane can contain at most $1$ point. The set should be as small as possible.

Point coordinates are all integers. Lines are given by two different points (with integer coordinates). Lines have a direction from their first point to their second point; this is used to determine that when a line intersects an input point, the input point is considered to be on the right side of the line.

Lines can only be horizontal, vertical or diagonal.

\heading{Input}

The first line contains a single integer $N$, the number of points.
Following $N$ lines describes the points.

The $(i+1)$-th line contains a pair of space separated integer coordinates $x$ and $y$ of the $i$-th point.

\heading{Output}

The first line should contain $L$, the number of lines.
Following $L$ lines describes lines.
The $(i+1)$-th line contains four space separated integers $X_1$, $Y_1$, $X_2$, $Y_2$. Points ($X_1$, $Y_1$) and ($X_2$, $Y_2$) must be different, the line goes through both of them. At least one of the following conditions must held:

\begin{itemize}
  \item $X_1 = X_2$ (vertical line)
  \item $Y_1 = Y_2$ (horizontal line)
  \item $X_1 - X_2 = Y_1 - Y_2$
  \item $X_1 - X_2 = Y_2 - Y_1$
\end{itemize}

Your solution should output at most $10\ 000$ lines and the absolute value of all coordinates must be less than or equall to $10\ 000$.

\heading{Scoring}
This is an open data problem. You can download all $10$ testcases from the submission system. You are only required to submit your output files.

If your output doesn't follow the output format or doesn't separate the points correctly, your score will be zero for the testcase.

Otherwise, your score for the testcase is equall to
$ 10 \cdot \left(1 - \sqrt{1 - L_{min} / L}\right)$,
where $L$ is the number of lines in your output and $L_{min}$ is the best submission made by any contestant.

\heading{Samples}

\sampleIN
4
3 1
4 5
6 6
8 4
\sampleOUT
3 2 8 7
2 8 8 2
\sampleEND

\end{document}
