\bigheading{Newspapers}

\authors{Błażej Magnowski}{Błażej Magnowski \& Marek Sommer}{Błażej Magnowski}

We will use binary search to solve this problem.
So now, we want to know if for a given value $S$, there exists in our tree a path of length at least $K$,
	such that the arithmetic average of its edges is equal to or greater then $S$.
Let's say that such a path exists and its length is equal to $N$.
Let's denote the values of the edges that lay on this path as $V_1, V_2, \ldots, V_N$.
Let's say that the value of the path is the sum of the values of the edges.
We know that:

\[\frac{V_1 + V_2 + \ldots + V_N}{N} \geqslant S\ \qquad | \cdot N \]
\[V_1 + V_2 + \ldots + V_N \geqslant NS\ \qquad | - NS\]
\[(V_1 - S) + (V_2 - S) + \ldots + (V_N - S) \geqslant 0\]

By subtracting $S$ from the values of edges we were able to change our to problem to finding out
	if the maximal value of the paths of length at least $K$ is equal to or greater then zero.
To solve this, we will use the same method that was used in task Universities.
We choose some vertex and find the maximal value of the paths of length at least $K$ which go through this vertex.
After that, we erase that vertex from our tree and continue our procedure in the subtrees.
The vertex we choose for the given subtree can be its centroid.
Due to that, all the subtrees created from removing that vertex will be at least
	two times smaller than the starting subtree.
If we can find the maximal value of the paths of length at least $K$
	which go through a vertex in a given subtree in linear time,
	the complexity of this part of the algorithm will be $O(N \log N)$.

\bigskip

Now, we need to know how to find the maximal value of the paths of length at least $K$ which go through a given vertex.
Let's name the given vertex $X$ and let's make this tree rooted in $X$.
Also let's call the path we are looking for the maximal path, and let's call the paths that start in $X$ tails.
At first, we need to compute the values of all the tails.
The maximal path consist of at most two tails.
Let's take any tail and assume that this path is one of the parts of the maximal path.
Let's say that $L$ is the length of this tail.
Then, the other part of the maximal path will be a path of length at least $K-L$
	which starts in $X$ and goes into a different subtree then the first tail.
Of course, the value of the other tail has to be maximal possible.
Let's say the length of the longest tail is equal to $M$.
We will construct an array $P$ and for every $i$ from $0$ to $M$, $P[i]$
	will hold two maximal values of tails of length $i$, which go into different subtrees.
With this array, for every $i$ from $0$ to $M$, we can compute two maximal values of tails
	of length at least $i$, which go into different subtrees.
Now, for every tail, we can assume that it is one of the tails of the maximal path,
	and add to it the most fitting tail in constant time.
So we will find the value of the maximal path in linear time.
Overall, the complexity of our solution is $O(N \log N \log D)$ where $D$ is the maximal value
	of an edge, divided by the relative or absolute error that is accepted.
